msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-15 paper.tex
Place bottlenecks+demography+multiple-mergers together
I think this is the subsection rearrangement that @JereKoskela suggested. Makes sense to me.

\subsection*{Simulation interface}
The majority of simulation packages are controlled either through
a command line interface~\citep[e.g.][]{hudson2002generating,kern2016discoal},
a text-based input file
format~\citep[e.g.][]{guillaume2006nemo,excoffier2011fastsimcoal,shlyakhter2014cosi2},
or a mixture of both.
Command line interfaces such as \ms\ make it very easy to run simple
simulations, but as model complexity and the number of parameters specified increases
they become difficult to understand and
error-prone~\citep{ragsdale2020lessons,gower2021demes}.
Specifying parameters through a text file alleviates this problem to a degree,
but lacks flexibility, for example, when running simulations with parameters
drawn from some distribution. In practice, for any significant simulation
project (or at least, any reproducible one), users will write a script
to generate the required command lines or input parameter files,
invoke the simulation engine, and process the results in some way.
This process is cumbersome and labour intensive, and packages
such \texttt{coala}~\citep{staab2016coala} have been developed
to allow simulations be run directly in a high-level
scripting language.

>>>>

\subsection*{Simulation interface}

The majority of simulation packages are controlled either through
a command line interface~\citep[e.g.][]{hudson2002generating,kern2016discoal},
a text-based input file
format~\citep[e.g.][]{guillaume2006nemo,excoffier2011fastsimcoal,shlyakhter2014cosi2},
or a mixture of both.
Command line interfaces such as \ms\ make it very easy to run simple
simulations, but as model complexity and the number of parameters specified increases
they become difficult to understand and
error-prone~\citep{ragsdale2020lessons,gower2021demes}.
Specifying parameters through a text file alleviates this problem to a degree,
but lacks flexibility, for example, when running simulations with parameters
drawn from some distribution. In practice, for any significant simulation
project (or at least, any reproducible one), users will write a script
to generate the required command lines or input parameter files,
invoke the simulation engine, and process the results in some way.
This process is cumbersome and labour intensive, and packages
such \texttt{coala}~\citep{staab2016coala} have been developed
to allow simulations be run directly in a high-level
scripting language.
